Nested sampling with two or more objective functions

### 2015-10-09 Paper/ms.tex
Working on algorithm

\begin{enumerate}
\item Generate $N$ particles $\{\xx_1, ..., \xx_N\}$ from $\pi(\xx)$.\\
\item Calculate the {\it corner count} (Equation~\ref{eqn:corner_count})
of each particle.\\
\end{enumerate}

@@

Need to be able to sort particles into a total order. Since $C_i$ is discrete,
each particle will also need a tiebreaker variable $a_i$ to accompany it.
For iteration 1, $\{(C_i, a_i)\}_{i=1}^N$ will provide the total ordering.
We exclude the corner with the lowest corner count.

For iteration 2, we need a new quantity for total order (I think?), which

>>>>

\begin{enumerate}
\item Generate $N$ particles $\{\xx_1, ..., \xx_N\}$ from $\pi(\xx)$.
\item Calculate the {\it corner count} (Equation~\ref{eqn:corner_count})
of each particle.
\item Choose one of the particles which has corner count equal to the
minimum nonzero value.
\end{enumerate}

@@
